### 2021-03-03 introduction.tex
Label
minor change

\section{Introduction}

Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices \cite{statcounter}. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}. Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms to identify privacy leaks, and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance. Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes. In this proposal, given an app A, a sandbox S identifies sensitive resources access by A, during dynamic and static analysis, and then block future calls to sensitive resources unidentified during this exploratory phase, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.

>>>>

\section{Introduction}\label{sec:introduction}

Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices \cite{statcounter}. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased~\cite{DBLP:journals/comsur/FarukiBLGGCR15,DBLP:journals/csur/SufatrioTCT15}. Security issues in Android software applications~\footnote{In this paper, we will use the terms Android Applications, Android Apps and Apps interchangeably, to represent Android software applications} have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, including the use of static analysis algorithms either to identify privacy leaks or to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}, for instance. Another approach explored by researchers to mitigate the same problem is the use of dynamic analysis to mine Android sandboxes. In this proposal, given an app A, a sandbox S identifies sensitive resources access by A, during dynamic and static analysis, and then block future calls to sensitive resources unidentified during this exploratory phase, thereby protecting Android users from malicious behavior.~\cite{DBLP:conf/icse/JamrozikSZ16}.
